### 2021-02-24 phd_2/article/article.tex
update bibliography

    Представленные численные примеры иллюстрируют, что предложенный алгоритм успешно справляется
    с нахождением численного решения задачи~\eqref{eq1}-\eqref{bc1}.

    \begin{thebibliography}{999}

        \bibitem{Modest}
        Modest~M.F.\ Radiative Heat Transfer.
        Academic Press.\ 2003.\ 822 p.

        \bibitem{Kovt}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D.
        Unique solvability of a steady-state complex heat transfer model
        // Commun. Nonlinear Sci. Numer. Simul. 2015. V.~20. N 3. P. 776--784.

        \bibitem{Pinnau07}
        R.~Pinnau. Analysis of Optimal Boundary Control for Radiative Heat
        Transfer Modelled by the SP$_1$-System~// Comm.
        Math. Sci. 2007. V.~5. N~4. P.~951--969.

        \bibitem{Tse12}
        Tse O., Pinnau R., Siedow N. Identification of temperature
        dependent parameters in laser--interstitial thermo therapy~//
        Math. Models Methods Appl. Sci. 2012. V.~22. N~9. P. 1--29.

        \bibitem{Kovt13}
        Kovtanyuk~A.E., Chebotarev~A.Yu. An iterative method for solving a
        complex heat transfer problem~// Appl.
        Math. Comput. 2013. V.~219. P.~9356--9362.

        \bibitem{Cheb14-1}
        Kovtanyuk~A.E., Chebotarev~A.Yu., Botkin~N.D., Hoffmann~K.-H. The
        unique solvability of a complex 3D heat transfer problem~// J.
        Math. Anal. Appl. 2014. V.~409. N~2. P.~808-815.

        \bibitem{JVM-14}
        Ковтанюк А.Е., Чеботарев А.Ю. Стационарная задача сложного теплообмена // Ж.
        вычисл. матем. и матем. физ. 2014. Т. 54. \textnumero~4. С. 711--719.

        \bibitem{Kovt14-2}
        Ковтанюк А.Е., Чеботарев А.Ю. Стационарная задача свободной конвекции с радиационным теплообменом // Дифференц.
        ур-ния. 2014. Т. 50. \textnumero~12. С. 1590--1597.

        \bibitem{Kovt14-3}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. Theoretical analysis of an optimal
        control problem of conductive-convective-radiative heat transfer // J. Math.
        Anal. Appl. 2014. V. 412. \textnumero~1. P. 520--528.

        \bibitem{Grenkin1}
        Гренкин Г.В., Чеботарев А.Ю. Нестационарная задача сложного теплообмена // Ж.
        вычисл. матем. и матем. физ. 2014. Т. 54. \textnumero~11. С. 1806--1816.

        \bibitem{Grenkin3}
        Гренкин Г.В., Чеботарев А.Ю. Неоднородная нестационарная задача сложного теплообмена // Сиб.
        электрон. матем. изв. 2015. Т. 12. С. 562--576.

        \bibitem{Grenkin4}
        Гренкин Г.В., Чеботарев А.Ю. Нестационарная задача свободной конвекции с радиационным теплообменом // Ж.
        вычисл. матем. и матем. физ. 2016. Т. 56. \textnumero~2. С. 275--282.

        \bibitem{Grenkin5}
        Grenkin G.V., Chebotarev A.Yu., Kovtanyuk A.E., Botkin N.D., Hoffmann K.-H. Boundary optimal control problem
        of complex heat transfer model // J. Math.
        Anal. Appl. 2016. V. 433. \textnumero~2. P. 1243--1260.

        \bibitem{JMAA-16}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. Optimal boundary control of a steady-state heat
        transfer model accounting for radiative effects // J. Math.
        Anal. Appl. 2016. V. 439. \textnumero~2. P. 678--689.

        \bibitem{AMC-16}
        Chebotarev A.Yu., Kovtanyuk A.E., Grenkin G.V., Botkin N.D., Hoffmann K.-H.
        Nondegeneracy of optimality conditions in control problems for a radiative-conductive heat transfer model
        // Appl.
        Math. Comput. 2016. V. 289. P. 371--380.

        \bibitem{JVM-16}
        Ковтанюк А.Е., Чеботарев А.Ю. Нелокальная однозначная разрешимость стационарной задачи сложного теплообмена
        // Ж.
        вычисл. матем. и матем. физ. 2016. Т. 56. \textnumero~5. С. 816--823.

        \bibitem{ESAIM}
        Chebotarev A.Yu., Grenkin G.V., Kovtanyuk A.E. Inhomogeneous steady-state problem of complex heat transfer //
        ESAIM Math.
        Model. Numer. Anal. 2017. V. 51. \textnumero~6. P. 2511--2519.

        \bibitem{JMAA-18}
        Chebotarev A.Yu., Grenkin G.V., Kovtanyuk A.E., Botkin N.D., Hoffmann K.-H. Inverse problem with finite
        overdetermination for steady-state equations of radiative heat exchange // J. Math.
        Anal. Appl. 2018. V. 460. \textnumero~2. P. 737--744.

        \bibitem{JMAA-19}
        Chebotarev A.Yu., Pinnau R. An inverse problem for a quasi-static approximate model of radiative heat transfer
        // J. Math.
        Anal. Appl. 2019. V. 472. \textnumero~1. P. 737--744.

        \bibitem{AmosA05}
        Амосов~А.А. Глобальная разрешимость одной нелинейной
        нестационарной задачи с нелокальным краевым условием типа
        теплообмена излучением~// Дифференц.
        ур-ния. Т.~41. N~1. 2005. С.~93--104.

        \bibitem{AmosA10}
        Amosov~A.A. Stationary nonlinear nonlocal problem of
        radiative-conductive heat transfer in a system of opaque bodies
        with properties depending on the radiation frequency~// J.
        Math. Sc. 2010. V.~164. N~3. P.~309--344.

@@

        \bibitem{Amosov17}
        Амосов А.А. Стационарная задача сложного теплообмена в системе полупрозрачных тел с краевыми условиями
        диффузного отражения и преломления излучения // Ж.
        вычисл. матем. и матем. физ. 2017. Т. 57. \textnumero~3. С. 510--535.

        \bibitem{Amosov17-1}
        Amosov A.A. Unique Solvability of Stationary Radiative - Conductive Heat Transfer
        Problem in a System of Semitransparent Bodies // J. of Math.
        Sc.(United States). 2017. V. 224. N~5. P.~618-646.

        \bibitem{Amosov18}
        Amosov A.A. Nonstationary problem of complex heat transfer in a system of
        semitransparent bodies with boundary-value conditions of diffuse reflection and refraction
        of radiation // J. of Math. Sc.(United States). 2018. V. 233. N~6. P.~777 -806.

        \bibitem{CNSNS19}
        Chebotarev A.Yu., Kovtanyuk A.E., Botkin N.D. Problem of radiation heat exchange with boundary conditions
        of the Cauchy type // Commun.
        Nonlinear Sci. Numer. Simul. 75 (2019) 262-269.

        \bibitem{CMMP20}
        Колобов А.Г., Пак Т.В., Чеботарев А.Ю. Стационарная задача радиационного теплообмена с граничными условиями
        типа Коши // Журнал вычислительной математики и математической физики.
        2019, том 59, № 7, с. 1258-1263.

@@

    \end{thebibliography}

\end{document}

>>>>

    Представленные численные примеры иллюстрируют, что предложенный алгоритм успешно справляется
    с нахождением численного решения задачи~\eqref{eq1}-\eqref{bc1}.
    %! Suppress = LineBreak
    \begin{thebibliography}{999}

        \bibitem{Pinnau07}
        Pinnau R. Analysis of optimal boundary control for radiative heat transfer modeled by $SP_1$-system //
        Commun. Math. Sci. 2007. V. 5. \textnumero~4. P. 951--969.

        \bibitem{AMC-13}
        Kovtanyuk A.E., Chebotarev A.Yu. An iterative method for solving a complex heat transfer problem // Appl. Math. Comput. 2013. V. 219. \textnumero~17. P. 9356--9362.
        \bibitem{Kovt14-1}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. The unique solvability of a complex 3D heat transfer problem // J. Math. Anal. Appl. 2014. V. 409. \textnumero~2. P. 808--815.
        \bibitem{JVM-14}
        Ковтанюк А.Е., Чеботарев А.Ю. Стационарная задача сложного теплообмена // Ж. вычисл. матем. и матем. физ. 2014. Т. 54. \textnumero~4. С. 711--719.
        \bibitem{Kovt14-2}
        Ковтанюк А.Е., Чеботарев А.Ю. Стационарная задача свободной конвекции с радиационным теплообменом // Дифференц. ур-ния. 2014. Т. 50. \textnumero~12. С. 1590--1597.
        \bibitem{Kovt14-3}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. Theoretical analysis of an optimal control problem of conductive-convective-radiative heat transfer // J. Math. Anal.
        Appl. 2014. V. 412. \textnumero~1. P. 520--528.
        \bibitem{Grenkin1}
        Гренкин Г.В., Чеботарев А.Ю. Нестационарная задача сложного теплообмена // Ж. вычисл. матем. и матем. физ. 2014. Т. 54. \textnumero~11. С. 1806--1816.
        \bibitem{CNSNS-15}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. Unique solvability of a steady-state complex heat transfer model // Commun. Nonlinear Sci. Numer. Simul. 2015. V. 20. \textnumero~3. P. 776--784.

        \bibitem{Grenkin3}
        Гренкин Г.В., Чеботарев А.Ю. Неоднородная нестационарная задача сложного теплообмена // Сиб. электрон. матем. изв. 2015. Т. 12. С. 562--576.
        \bibitem{Grenkin4}
        Гренкин Г.В., Чеботарев А.Ю. Нестационарная задача свободной конвекции с радиационным теплообменом // Ж. вычисл. матем. и матем. физ. 2016. Т. 56. \textnumero~2. С. 275--282.
        \bibitem{Grenkin5}
        Grenkin G.V., Chebotarev A.Yu., Kovtanyuk A.E., Botkin N.D., Hoffmann K.-H. Boundary optimal control problem of complex heat transfer model // J. Math. Anal. Appl. 2016. V. 433. \textnumero~2. P. 1243--1260.

        \bibitem{JMAA-16}
        Kovtanyuk A.E., Chebotarev A.Yu., Botkin N.D., Hoffmann K.-H. Optimal boundary control of a steady-state heat transfer model accounting for radiative effects // J. Math. Anal. Appl.
        2016. V. 439. \textnumero~2. P. 678--689.
        \bibitem{AMC-16}
        Chebotarev A.Yu., Kovtanyuk A.E., Grenkin G.V., Botkin N.D., Hoffmann K.-H\@.
        Nondegeneracy of optimality conditions in control problems for a radiative-conductive heat transfer model // Appl. Math. Comput. 2016. V. 289. P. 371--380.
        \bibitem{JVM-16}
        Ковтанюк А.Е., Чеботарев А.Ю. Нелокальная однозначная разрешимость стационарной задачи сложного теплообмена // Ж. вычисл. матем. и матем. физ. 2016. Т. 56. \textnumero~5. С. 816--823.
        \bibitem{ESAIM}
        Chebotarev A.Yu., Grenkin G.V., Kovtanyuk A.E. Inhomogeneous steady-state problem of complex heat transfer // ESAIM Math. Model. Numer. Anal. 2017. V. 51. \textnumero~6. P. 2511--2519.

        \bibitem{CNSNS18}
        Chebotarev, A.Y., Grenkin, G.V., Kovtanyuk, A.E., Botkin, N.D., Hoffmann, K.-H. Diffusion approximation of the radiative-conductive heat transfer model with Fresnel matching conditions// Communications in Nonlinear Science and Numerical Simulation. 57 (2018) 290-298.

        \bibitem{JMAA-18}
        Chebotarev A.Yu., Grenkin G.V., Kovtanyuk A.E., Botkin N.D., Hoffmann K.-H. Inverse problem with finite overdetermination for steady-state equations of radiative heat exchange // J. Math. Anal. Appl. 2018. V. 460. \textnumero~2. P. 737--744.
        \bibitem{JMAA-19}
        Chebotarev A.Yu., Pinnau R. An inverse problem for a quasi-static approximate model of radiative heat transfer // J. Math. Anal. Appl. 2019. V. 472. \textnumero~1. P. 314--327.
        \bibitem{JVM-19-INV} Гренкин Г.В., Чеботарев А.Ю. Обратная задача для уравнений сложного теплообмена // Журнал вычислительной математики и математической физики. 2019, том 59, N 8, с. 1420-1430.

        \bibitem{CNSNS19}
        Chebotarev A.Y., Kovtanyuk A.E., Botkin N.D. Problem of radiation heat exchange with boundary conditions of the Cauchy type // Communications in Nonlinear Science and Numerical Simulation. 75 (2019) 262-269.

        \bibitem{CMMP20}
        Колобов А.Г., Пак Т.В., Чеботарев А.Ю.
        Стационарная задача радиационного теплообмена с граничными условиями типа Коши
        // Журнал вычислительной математики и математической физики.
        2019, том 59, N 7, с. 1258--1263.

        \bibitem{Amosov05}
        Амосов~А.А. Глобальная разрешимость одной нелинейной
        нестационарной задачи с нелокальным краевым условием типа
        теплообмена излучением~// Дифференц. ур-ния. Т.~41. N~1.
        2005. С.~93--104.

        \bibitem{Amosov10}
        Amosov~A.A. Stationary nonlinear nonlocal problem of
        radiative-conductive heat transfer in a system of opaque bodies
        with properties depending on the radiation frequency~// J\@.
        Math. Sc. 2010. V.~164. N~3. P.~309--344.

@@

        \bibitem{Amosov17}
        Amosov A.A. Unique Solvability of Stationary Radiative - Conductive Heat Transfer
        Problem in a System of Semitransparent Bodies // J. of Math. Sc.(United
        States). 2017. V. 224. N~5. P.~618-646.

        \bibitem{Amosov20-1}
        Amosov, A.A. Asymptotic Behavior of a Solution to the Radiative Transfer Equation in a Multilayered Medium with Diffuse Reflection and Refraction Conditions // J Math Sci 244, 541-575 (2020).

        \bibitem{Amosov20}
        Amosov A.A., Krymov N.E. On a Nonstandard Boundary Value Problem Arising in Homogenization of Complex Heat Transfer Problems // J. of Math. Sc.(United
        States). 2020. V. 244. P.~357 - 377.

@@

    \end{thebibliography}
\end{document}
